On First-order Proofs without syntax

### 2020-12-21 main.tex
Add the style file

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{natbib}

\parindent=0pt % indent spacing
\parskip=0.6em % spacing between two paragraphs
\setlength{\bibsep}{1.2ex} % bibliography vertical spacing

\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

\title{On first-order combinatorial proofs}
\author{Jui-Hsuan Wu, Lutz Strassburger}

\begin{document}

\maketitle

@@

\begin{theorem_}
\label{thm1}
Let $\Gamma$ be a sequent. Then there is a proof of $\Pi$ in {\bf LK} + $mix$ iff there is a proof of some sequent $\Delta$ in {\bf MLL1} + $mix$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only. 
\end{theorem_}

@@

($\Leftarrow$)
We regard the proof in {\bf MLL1} + $mix$ as a proof in {\bf LK} + $mix$.
Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in {\bf LK} + $mix$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
For the $\cD$ part, the only non-trivial case is the permutation with the $\vee$ rule where the formula generated is $A \vee A$.

@@

\iffalse

Now consider a proof $\Pi$ of some sequent $\Gamma$ in {\bf LK}:
The observation above gives the possibility of
transforming the proof into a proof in {\bf MLL} followed by a derivation consisting
of the $\cD$ and $\wD$ rules only.

Conversely, consider a proof $\Pi$ of some sequent $\Gamma$ consisting of a
proof $\Pi'$ in {\bf LK} followed by a derivation $\Pi''$ consisting
the $\cD$ and $\wD$ rules only. 
We can assume that the proof $\Pi'$ is cut-free and contains only atomic
axioms.
Now consider some instance of $\cD$ in the derivation $\Pi''$:
\begin{prooftree}
  \hypo{S\{A \vee A\}} 
  \infer1[$\cD$]{S\{A\}}
\end{prooftree}

If the subformula $A \vee A$ is erased at some point by the $\wD$ rule:

\begin{center}
\begin{prooftree}
  \hypo{\vdash T\{\fff\}}
  \infer1[$\wD$]{\vdash T\{B\}}
  \ellipsis{$\mathcal{D}$}{\vdash S\{A \vee A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
\end{prooftree}
\end{center}

where $A \vee A$ is a subformula of $B$, then we can erase the instance of $\cD$
rule considered
and obtain the derivation:

\begin{center}
\begin{prooftree}
  \hypo{\vdash T\{\fff\}}
  \infer1[$\wD$]{\vdash T\{B[A \vee A \leftarrow A]\}}
  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{\vdash S\{A\}}
\end{prooftree}
\end{center}

where $B[A \vee A \leftarrow A]$ (resp. $\mathcal{D}[A \vee A \leftarrow A]$) is the
formula (resp. derivation) obtained from $B$ (resp. $\mathcal{D}$) by replacing every
occurrence of $A \vee A$ with $A$.

Now suppose that the subformula $A \vee A$ is not erased in the derivation
$\Pi''$.

Since there is the contraction rule $ctr$, the subformula $A \vee A$ might be duplicated in the proof $\Pi'$. We now consider a branch of the proof $\Pi'$

Since $\Pi'$ is cut-free, it enjoys the subformula property and since all axioms
are atomic, the "subformula" $A \vee A$ should be decomposed at some point in the
proof and thus the proof $\Pi$ should be of the following form:

\begin{center}
\begin{prooftree}
  \hypo{\cdots}
  \hypo{\vdash \Gamma, A, A}
  \infer1[$\vee$]{\vdash \Gamma, A \vee A}
  \ellipsis{$\mathcal{D}$}{}
  \infer2[]{\vdash T\{A \vee A\}}
  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
\end{prooftree}
\end{center}

where $\Pi'$ =
\begin{prooftree}
  \hypo{\vdash T\{A \vee A\}}
  \ellipsis{}{\vdash \Gamma}
\end{prooftree}

We can thus to apply the $ctr$ rule first and to replace each occurrence of $A
\vee A$ in the derivation (branch) $\mathcal{D}$:

\begin{center}
\begin{prooftree}
  \hypo{\cdots}
  \hypo{\vdash \Gamma, A, A}
  \infer1[$ctr$]{\vdash \Gamma, A}
  \ellipsis{$\mathcal{D}[A \vee A \leftarrow A]$}{}
  \infer2[]{\vdash T\{A \vee A\}}
  \ellipsis{$\mathcal{D}_1$}{\vdash S\{A \vee A\}}
  \infer1[$\cD$]{\vdash S\{A\}}
  \ellipsis{$\mathcal{D}_2$}{\vdash \Gamma}
\end{prooftree}
\end{center}

By applying the same process to all the branches of occurrences of $A \vee A$,
we obtain a proof of $\Gamma$ without the instance
\begin{prooftree}
  \hypo{S\{A \vee A\}}
  \infer1[$\cD$]{S\{A\}}
\end{prooftree}
of the $\cD$ rule. The derivation $\Pi'$ can be replaced by the following:
\begin{center}
\begin{prooftree}
  \hypo{\vdash T\{A\}}
  \ellipsis{$\mathcal{D}_1[A \vee A \leftarrow A]$}{\vdash S\{A\}}
  \ellipsis{$\mathcal{D}_2[A \vee A \leftarrow A]$}{\vdash \Gamma}
\end{prooftree}
\end{center}

We can thus eliminate all the instances of the $\cD$ rule in the proof. Suppose
now that the derivation $\Pi''$ consists of the $\wD$ rule only.

[PROOF TO DO]

\fi

D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
unification nets with respect to {\bf MLL1} + $mix$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\begin{proposition}
If one of the switching graphs of the unification structure of $\phi$
contains a cycle or is not connected, then there exists an induced bimatching of the
corresponding linked fograph.

\begin{proof}

We use frames introduced by Hughes in Section 4 of \cite{Hughes 2015}.

\begin{definition}
Let $\theta$ be a unification structure on an {\bf MLL1} sequent $\Gamma$.
We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an {\bf MLL} sequent $\Gamma_m$:

@@

\begin{center}
\mbox{
\begin{tikzpicture}
  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
  \draw (0, 0) node (par1) {$\parr$};
  \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
  \draw (-1.8, 1.2) node (par2) {$\parr$};
    \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
    \draw (-0.8, 2.4) node (y) {$\exists y$};
    \draw (-2.8, 3.6) node (px) {$\overline{p}x$};
    \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
    \draw (1.8, 2.4) node (tens) {$\otimes$};
    \draw (0.8, 3.6) node (pz) {$pz$};
    \draw (2.8, 3.6) node (qfz) {$qfz$};
    \draw (par1) -- (par2) [<-];
    \draw (par1) -- (z) [<-];
    \draw (par2) -- (x) [<-]; 
    \draw (par2) -- (y) [<-];
    \draw (x) -- (px) [<-]; 
    \draw (y) -- (qy) [<-];
    \draw (z) -- (tens) [<-]; 
    \draw (tens) -- (pz) [<-];
    \draw (tens) -- (qfz) [<-];
    \draw (y) -- (z) [dotted, ->];
    \draw (x) -- (z) [dotted, ->];
    \draw[color=blue, dashed] (px) to [bend left] (pz);
    \draw[color=red, dashed] (qy) to [bend left] (qfz);
\end{tikzpicture}
\hspace{0.5cm}

\begin{tikzpicture}
  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
  \draw (0, 0) node (par1) {$\parr$};
  \draw (1, 0.9) node (par3) {\color{blue} $\parr$};
  \draw (-1.8, 1.2) node (par2) {$\parr$};
  \draw (-2.6, 2.4) node (tens1) {\color{red} $\otimes$};
  \draw (-1, 2.4) node (tens2) {$\otimes$};
  \draw (-2.2, 3.6) node (S) {\color{red} $S$};
  \draw (-0.6, 3.6) node (R) {$R$};
  \draw (-3, 3.6) node (nP) {$\overline{P}$};
  \draw (-1.4, 3.6) node (nQ) {$\overline{Q}$};
  \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
  \draw (1.6, 1.8) node (par4) {$\parr$};
  \draw (2.2, 2.7) node (tens3) {$\otimes$};
  \draw (2, 3.6) node (P) {$P$};
  \draw (2.8, 3.6) node (Q) {$Q$};
  \draw (1.2, 3.6) node (nR) {$\overline{R}$};
  \draw (par2) -- (par1) [->];
  \draw (par3) -- (par1) [->];
  \draw (tens1) -- (par2) [->];
  \draw (tens2) -- (par2) [->];
  \draw (nP) -- (tens1) [->];
  \draw (S) -- (tens1) [->, color=red];
  \draw (nQ) -- (tens2) [->];
  \draw (R) -- (tens2) [->];
  \draw (nS) -- (par3) [->, color=blue];
  \draw (nR) -- (par4) [->];
  \draw (tens3) -- (par4) [->];
  \draw (P) -- (tens3) [->];
  \draw (Q) -- (tens3) [->];
  \draw (par4) -- (par3) [->];
  \draw (nP) to [bend left] (P);
  \draw (nQ) to [bend left] (Q);
  \draw (S) to [bend left] (nS);
  \draw (R) to [bend left] (nR);
\end{tikzpicture}
}

{\bf Figure 8.} The unification net in Example \ref{exunif} and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
\end{center}

@@

\iffalse
Consider a switching graph.
We associate to this switching graph a proof net for {\bf MLL} by replacing quantifiers with fresh atoms and dependencies with new axiom links using the following schema:

\begin{center}	
\mbox{
    \begin{tikzpicture}
    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
    \draw (0, -2) node (existsx) {$\exists x$};
    \draw (0, 0) node (A) {$A$};
    \draw (existsx) -- (A) ;
    \end{tikzpicture}

    \vspace{0.5cm}
    \begin{tikzpicture}
    \draw (0, 1) node
    {$\leadsto$};
    \draw (0, 2) node {};
    \draw (0, 0) node {};
    \end{tikzpicture}
    \vspace{0.5cm}

    \begin{tikzpicture}
    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
    \draw (0, 0) node (existx) {$E_x$};
    \draw (1.2, -2) node (tens) {$\otimes$};
    \draw (2.4, 0) node (A) {$A$};
    \draw (tens) -- (A);
    \draw (tens) -- (existx);
    \end{tikzpicture}
}
\vspace{0.3cm}

\mbox{
    \begin{tikzpicture}
    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
    \draw (0, -2) node (forallx) {$\forall x$};
    \draw (0, 0) node (A) {$A$};
    \draw (forallx) -- (A) ;
    \end{tikzpicture}

    \vspace{0.5cm}
    \begin{tikzpicture}
    \draw (0, 1) node
    {$\leadsto$};
    \draw (0, 2) node {};
    \draw (0, 0) node {};
    \end{tikzpicture}
    \vspace{0.5cm}

    \begin{tikzpicture}
    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
     \draw (0, 0) node (Ux) {$U_x$};
    \draw (1.2, -2) node (parr) {$\parr$};
    \draw (2.4, 0) node (A) {$A$};
    \draw (parr) -- (A);
    \draw (parr) -- (Ux);
    \end{tikzpicture}
}

\mbox{
    \begin{tikzpicture}
    \tikzstyle{every node}=[circle, minimum size=12pt, inner sep=2pt]
    \draw (-2, -2) node (existsx) {$\exists x$};
    \draw (-2, 0) node (A) {$A$}; 
    \draw (0, -2) node (forally) {$\forall y$};
    \draw (0, 0) node (B) {$B$};
    \draw (forally) -- (B);
    \draw (existsx) -- (A);
    \draw[->] (existsx) -- (forally);
    \end{tikzpicture}

    \vspace{0.5cm}
    \begin{tikzpicture}
    \draw (0, 1) node
    {$\leadsto$};
    \draw (0, 2) node {};
    \draw (0, 0) node {};
    \end{tikzpicture}
    \vspace{0.5cm}

    \begin{tikzpicture}
    \tikzstyle{every node}=[draw, circle, minimum size= 12 pt, inner sep=3pt]
    \draw (4.8, 0) node (Uy) {$U_y$};
    \draw (6, -2) node (parr) {$\parr$};
    \draw (7.2, 0) node (B) {$B$};
    \draw (parr) -- (B);
    \draw (parr) -- (Uy);
    \draw (2.4, 0) node (existx) {$E_x$};
    \draw (1.2, -2) node (tens) {$\otimes$};
    \draw (0, 0) node (A) {$A$};
    \draw (tens) -- (A);
    \draw (tens) -- (existx);
    \draw (3.6, 2) node (ax) {$ax$};
    \draw (ax) to [bend right] (existx);
    \draw (ax) to [bend left] (Uy);

    \end{tikzpicture}
}
\end{center}
\fi

\iffalse

\begin{proof}
Let $C$ be a cycle contained in a switching graph. We can suppose that $C$ is
minimum, i.e., for all $V' \subsetneq V $, there is no cycle going through exactly $V'$ in a switching graph of the unification structure, where $V$ is the set of vertices of $C$.

Now write $C$ as the
concatenation of $l_1, p_1, l_2, p_2, ..., l_n, p_n$ where the $l_i$ are
leaps and the $p_i$ are paths consisting of the other edges. We first prove that
for all $i$, $p_i$ is non-empty.

Suppose that $p_k$ is empty. The only possible case is:
\begin{center}
\begin{tikzpicture}
  \node (x0) at (0, 0) {$\forall y$};
  \node (x1) at (2, 0) {$\exists x$};
  \node (x2) at (4, 0) {$\forall z$}; 
  \draw [->] (x1) -- (x0) node [midway, above=7pt] {$l_k$};
  \draw [->] (x1) -- (x2) node [midway, above=7pt] {$l_{k+1}$};
\end{tikzpicture}
\end{center}

This means that every unifier of the unification structure assigns a term
containing $y$ and $z$ to the existential binder $x$, which also implies
the existence of an atom which is a descendant of the $\exists x$. Without loss of
generality, we can assume that the predual of this atom is in the scope
of $\forall y$, then it must contain $y$ and $z$, which is contradictory.

Hence, all the $p_i$ are non-empty.

>>>>

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% *** PACKAGES *** %

\usepackage[utf8]{inputenc}
\usepackage{ebproof}
\usepackage{amsmath}
\usepackage{ebproof}
\usepackage{virginialake}
\usepackage{cmll}
\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsthm}\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]

@@

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% *** MACROS ***

% ** SYSTEMS **

\newcommand*{\LK}{\mathsf{LK}}
\newcommand*{\LKm}{\mathsf{LK + mix}}
\newcommand*{\MLL}{\mathsf{MLL}}
\newcommand*{\FOMLL}{\mathsf{MLL1}} 
\newcommand*{\FOMLLm}{\mathsf{MLL1 + mix}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{On First-order Proofs without syntax}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Dominic J. D. Hughes}
\IEEEauthorblockA{}
\and
\IEEEauthorblockN{Lutz Straßburger}
\IEEEauthorblockA{Inria, Equipe Partout\\
Ecole Polytechnique\\
LIX UMR 7161\\
France}
\and
\IEEEauthorblockN{Jui-Hsuan Wu}
\IEEEauthorblockA{Ecole Normale Supérieure\\
France}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

\begin{theorem_}
\label{thm1}
Let $\Gamma$ be a sequent. Then there is a proof of $\Pi$ in $\LKm$ iff there is a proof of some sequent $\Delta$ in $\FOMLLm$ and a derivation from $\Delta$ to $\Gamma$ consisting of the $\cD$ and $\wD$ rules only. 
\end{theorem_}

@@

($\Leftarrow$)
We regard the proof in $\FOMLLm$ as a proof in $\LKm$.
Then we put the derivation consisting of only $\cD$ and $\wD$ under the proof in $\LKm$. Now we try to permute all the instances $\cD$ and $\wD$ upwards with the rules of LK and $mix$. 
For the $\cD$ part, the only non-trivial case is the permutation with the $\vee$ rule where the formula generated is $A \vee A$.

@@

D. Hughes proves in \cite{Hughes 2019} the soundness and completeness of
unification nets with respect to $\FOMLLm$. In the following, we establish the
equivalence between unification nets and fonets.

@@

\begin{proposition}
If one of the switching graphs of the unification structure of $\phi$
contains a cycle or is not connected, then there exists an induced bimatching of the
corresponding linked fograph.
\begin{proof}
We use frames introduced by D. Hughes in Section 4 of \cite{Hughes 2015}.

\begin{definition}
Let $\theta$ be a unification structure on an $\FOMLL$ sequent $\Gamma$.
We define the \textit{frame}  of $\theta$ by exhaustively applying the following subformula rewriting steps, to obtain a proof structure $\theta_m$ on an $\MLL$ sequent $\Gamma_m$:

@@

\begin{center}
\begin{tikzpicture}
  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
  \draw (0, 0) node (par1) {$\parr$};
  \draw (1.8, 1.2) node (z) {\color{blue} $\forall z$};
  \draw (-1.8, 1.2) node (par2) {$\parr$};
    \draw (-2.8, 2.4) node (x) {\color{red} $\exists x$};
    \draw (-0.8, 2.4) node (y) {$\exists y$};
    \draw (-2.8, 3.6) node (px) {$\overline{p}x$};
    \draw (-0.8, 3.6) node (qy) {$\overline{q}y$};
    \draw (1.8, 2.4) node (tens) {$\otimes$};
    \draw (0.8, 3.6) node (pz) {$pz$};
    \draw (2.8, 3.6) node (qfz) {$qfz$};
    \draw (par1) -- (par2) [<-];
    \draw (par1) -- (z) [<-];
    \draw (par2) -- (x) [<-]; 
    \draw (par2) -- (y) [<-];
    \draw (x) -- (px) [<-]; 
    \draw (y) -- (qy) [<-];
    \draw (z) -- (tens) [<-]; 
    \draw (tens) -- (pz) [<-];
    \draw (tens) -- (qfz) [<-];
    \draw (y) -- (z) [dotted, ->];
    \draw (x) -- (z) [dotted, ->];
    \draw[color=blue, dashed] (px) to [bend left] (pz);
    \draw[color=red, dashed] (qy) to [bend left] (qfz);
\end{tikzpicture}
\vspace{0.5cm}

\begin{tikzpicture}
  \tikzstyle{every node}=[circle, minimum size=20pt, inner sep=2pt]
  \draw (0, 0) node (par1) {$\parr$};
  \draw (1, 0.9) node (par3) {\color{blue} $\parr$};
  \draw (-1.8, 1.2) node (par2) {$\parr$};
  \draw (-2.6, 2.4) node (tens1) {\color{red} $\otimes$};
  \draw (-1, 2.4) node (tens2) {$\otimes$};
  \draw (-2.2, 3.6) node (S) {\color{red} $S$};
  \draw (-0.6, 3.6) node (R) {$R$};
  \draw (-3, 3.6) node (nP) {$\overline{P}$};
  \draw (-1.4, 3.6) node (nQ) {$\overline{Q}$};
  \draw (0.4, 3.6) node (nS) {\color{blue} $\overline{S}$};
  \draw (1.6, 1.8) node (par4) {$\parr$};
  \draw (2.2, 2.7) node (tens3) {$\otimes$};
  \draw (2, 3.6) node (P) {$P$};
  \draw (2.8, 3.6) node (Q) {$Q$};
  \draw (1.2, 3.6) node (nR) {$\overline{R}$};
  \draw (par2) -- (par1) [->];
  \draw (par3) -- (par1) [->];
  \draw (tens1) -- (par2) [->];
  \draw (tens2) -- (par2) [->];
  \draw (nP) -- (tens1) [->];
  \draw (S) -- (tens1) [->, color=red];
  \draw (nQ) -- (tens2) [->];
  \draw (R) -- (tens2) [->];
  \draw (nS) -- (par3) [->, color=blue];
  \draw (nR) -- (par4) [->];
  \draw (tens3) -- (par4) [->];
  \draw (P) -- (tens3) [->];
  \draw (Q) -- (tens3) [->];
  \draw (par4) -- (par3) [->];
  \draw (nP) to [bend left] (P);
  \draw (nQ) to [bend left] (Q);
  \draw (S) to [bend left] (nS);
  \draw (R) to [bend left] (nR);
\end{tikzpicture}

{\bf Figure 8.} A unification net and its frame. The colored part shows how the dependency ${\color{red} \exists x} \rightarrow {\color{blue} \forall z}$ is transformed.
\end{center}

@@

\end{proof}
\end{proposition}
